%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee 
% that it will correctly compile on your system if you have a non-standard  
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{letter}
\usepackage{fontspec} 

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}
\usepackage[usenames,dvipsnames]{color}
% FONTS
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode
\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Hoefler Text}
\setmonofont[Scale=0.8]{Bitstream Vera Sans Mono} 
\setsansfont[Scale=0.9]{Optima Regular} 
% ---- CUSTOM AMPERSAND
\newcommand{\amper}{{\fontspec[Scale=.95]{Hoefler Text}\selectfont\itshape\&}}
% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[xetex, bookmarks, colorlinks, breaklinks, pdftitle={Curriculum Vitae},pdfauthor={Eliza Weisman}]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} 
\signature{Eliza Weisman}
\address{990 First St.\\
Meadville, PA, \texttt{16335}\\
U.S.A.\\[.2cm]
Phone: \texttt{+1 (814)-853-1501}\\
%Fax: \texttt{609-924-8399}\\[.2cm]
Email: \href{mailto:eliza@elizas.website}{\texttt{eliza@elizas.website}}}
% DOCUMENT
\begin{document}

\begin{letter}{
EYEBEAM \\
34 35th St. \\
5th Fl, Unit 26 \\
Brooklyn, NY, \texttt{11232}
}
\opening{Dear Search Committee,}

Please accept the enclosed documents as an application for the Creative Technology Intern position for the summer of 2017.

My artistic works engage with the themes of mysticism, the technoculture, and social criticism, through a combination of interactive art, installation, and performance. Making extensive use of new media and emerging technologies, my work also engages critically with the culture of these forms. I have studied digital media from both the perspective of art-making and that of computer science, and draw upon both to inform my artistic practice both technically and aesthetically. Furthermore, I have experience using electronics, embedded systems, robotics, and Internet of Things technologies, video, photography, and the biological sciences as modes of artistic expression. The art-making and research that Eyebeam facilitates is directly in line with my interests and skills.

Previously, I have...
\closing{Sincerely.}
\end{letter}

\end{document}